Ants-Review: A Protocol For Open Anonymous Peer-Reviews\thanks{Supported by ETHTurin}

### 2020-06-03 paper-v0.tex
small changes

\section{Conclusion and Discussions}
In this whitepaper we addressed a central problem within the quality control academic dissemination: the peer-review process. We showed how blockchain technology could provide an efficient and viable solution and open up possibile directions for a change in paradigm in scientific communication. We proposed an incentive mechanism that could solve the problems of lack of acknowledgment and trust during peer-review. We exposed the architecture of our project and our Proof of Concept (PoC) for which we adopted cutting-edge tools from the open source blockchain community.

\section{Supplementary material}
Our open source code is available at the Github repository. A demo of the project is available at Youtube channel.
\section{CRediT Authorship Contribution Statement}
Bianca Trovò: Conceptualization, Investigation, Visualization, Writing - original draft, Writing - review & editing. Nazzareno Massari: Project administration, Methodology, Validation, Software development. Both authors equally contributed and supervised the project.
\section{Declaration of Competing Interest}
The authors declare no competing interests.

>>>>

\section{Conclusion and Discussions}
In this whitepaper we addressed a central problem within the quality control academic dissemination: the peer-review process. We showed how blockchain technology could provide an efficient and viable solution and open up possibile directions for a change in paradigm in scientific communication. We proposed an incentive mechanism that could solve the problems of lack of acknowledgment and trust during peer-review. We exposed the architecture of our project and our Proof of Concept (PoC) for which we adopted cutting-edge tools from the open source blockchain ecosystem.

\section{Supplementary material}
The source code is open and available at the Github repository. A demo of the project is available at Youtube channel.
\section{CRediT Authorship Contribution Statement}
Bianca Trovò: Conceptualization, Investigation, Visualization, Writing - original draft, Writing - review & editing. Nazzareno Massari: Project administration, Methodology, Validation, Software development. Both authors equally contributed and supervised the project.
\section{Declaration of Competing Interest}
The authors declare no competing interests.
